\textbf{Using the MSU Thesis Class}

### 2022-03-25 msu-thesis.tex
v3.1b added flag for single appendix so that the counter remains in the chapter but doesn't appear in the chapter title;  Fixes #14

\def\msuversion{3.1}
\def\msudate{2022/03/03}
\title{\textbf{Using the MSU Thesis Class}}
\author{\textbf{Alan Munn}\\Department of Linguistics and Languages\\\texttt{\href{mailto:amunn@msu.edu}{amunn@msu.edu}}}
\date{Version \msuversion\\\msudate}
\usepackage[T1]{fontenc}
\usepackage[lmargin=.75in,rmargin=.75in,tmargin=1in,bmargin=1in]{geometry}
\usepackage{titling}
\usepackage{array, booktabs, multicol, fancyhdr, xspace,tabularx}
\usepackage{enumitem}
\usepackage{fancyvrb,listings,url}
\usepackage[sf]{titlesec}
\usepackage[colorlinks=true]{hyperref}

@@

\subsection{Algorithm packages\label{algorithms}}
Because the various algorithm formatting packages such as \pkg{algorithm2e} and \pkg{algorithmicx} (or its related packages) sometimes create incompatibilities with the \pkg{memoir} float methods, the class provides you with floating |{algorithm}| environment and the corresponding list of algorithms, so you do not have to create your own list of algorithms. Here are some specific important points about using \pkg{algorithm2e} and \pkg{algorithmicx}.
\begin{itemize}[label=\textbullet]
\item Do \emph{not} load the \pkg{algorithm} package.
\item If you use the \pkg{algorithm2e} package you \emph{must} load it with the |[algo2e]| option (along with any other options you need).
\end{itemize}
\subsubsection{\pkg{algorithmicx} package} If you are using the \pkg{algorithmicx} package, any of its related packages (including its older predecessor \pkg{algorithmic}) which suggest that you use the \pkg{algorithm} package to create floating algorithms, you can load the \pkg{float} package to use the its float styling capabilities instead of loading the \pkg{algorithm} package. You should \emph{not} however use the \pkg{float} package to create new floating environments. You must use the \pkg{memoir} methods to create new floating environments and only then load the \pkg{float} package.

@@

Thanks to Lars Madsen, Ulrike Fischer and Peter Wilson for help with setting up parts of the memoir code for versions 1.0--1.4 (now eliminated due to changed requirements). Thanks to Wolfgang Sternefeld for supplying the \pkg{linguex} spacing fix code, Leo Liu for the landscape page numbering code, which greatly simplified my original version, and Florent Chervet for the \pkg{hyperref} code. Thanks also to the following students who have reported problems over the years: Irina Agafonova, Ali Al-jiboory, Julian Blank, Dmitriy Bryndin, Greg Christian, Kyle Crayne, Ciaron Hamilton, Matt Husband, Changkuk Jung, Adam Liter, William Muir, Alicia Parrish, Neil ver Planck, Adam Soliman, Erik Stitt, Michael Wojcik, Eremey Valetov, Matthew Vincent and Yisu Zhou. A special thank you to Non Thongprong who graciously provided a copy of his entire thesis which allowed me to debug some especially subtle spacing inconsistencies.

>>>>

\def\msuversion{3.1b}
\def\msudate{2022/03/25}
\title{\textbf{Using the MSU Thesis Class}}
\author{\textbf{Alan Munn}\\Department of Linguistics, Languages, and Cultures\\Michigan State University\\\texttt{\href{mailto:amunn@msu.edu}{amunn@msu.edu}}}
\date{Version \msuversion\\\msudate}
\usepackage[T1]{fontenc}
\usepackage[lmargin=.75in,rmargin=.75in,tmargin=1in,bmargin=1in]{geometry}
\usepackage{titling}
\usepackage{array, booktabs, multicol, fancyhdr, xspace,tabularx}
\usepackage{enumitem}
\usepackage{fancyvrb,listings,url}
\usepackage[sf]{titlesec}
\usepackage[colorlinks=true]{hyperref}

@@

\subsection{Algorithm packages\label{algorithms}}
Because the various algorithm formatting packages such as \pkg{algorithm2e} and \pkg{algorithmicx} (or its related packages) sometimes create incompatibilities with the \pkg{memoir} float methods, the class provides you with a floating |{algorithm}| environment and the corresponding list of algorithms, so you do not have to create your own list of algorithms. Here are some specific important points about using \pkg{algorithm2e} and \pkg{algorithmicx}.
\begin{itemize}[label=\textbullet]
\item Do \emph{not} load the \pkg{algorithm} package.
\item If you use the \pkg{algorithm2e} package you \emph{must} load it with the |[algo2e]| option (along with any other options you need).
\end{itemize}
\subsubsection{\pkg{algorithmicx} package} If you are using the \pkg{algorithmicx} package, any of its related packages (including its older predecessor \pkg{algorithmic}) which suggest that you use the \pkg{algorithm} package to create floating algorithms, you can load the \pkg{float} package to use the its float styling capabilities instead of loading the \pkg{algorithm} package. You should \emph{not} however use the \pkg{float} package to create new floating environments. You must use the \pkg{memoir} methods to create new floating environments and only then load the \pkg{float} package.

@@

Thanks to Lars Madsen, Ulrike Fischer and Peter Wilson for help with setting up parts of the memoir code for versions 1.0--1.4 (now eliminated due to changed requirements). Thanks to Wolfgang Sternefeld for supplying the \pkg{linguex} spacing fix code, Leo Liu for the landscape page numbering code, which greatly simplified my original version, and Florent Chervet for the \pkg{hyperref} code. Thanks also to the following students who have reported problems over the years: Irina Agafonova, Ali Al-jiboory, Julian Blank, Dmitriy Bryndin, Greg Christian, Kyle Crayne, Ciaron Hamilton, Matt Husband, Changkuk Jung, Adam Liter, William Muir, Alicia Parrish, Neil ver Planck, Adam Soliman, Erik Stitt, Eremey Valetov, Matthew Vincent, Michael Wojcik,  Stephen Yuwono, and Yisu Zhou. A special thank you to Non Thongprong who graciously provided a copy of his entire thesis which allowed me to debug some especially subtle spacing inconsistencies.
